Tropical Andes plant occurrence data GBIF

### 2023-09-20 code/L0/L0_TropicalAndes_plants_GBIF.Rmd
update GBIF call to correct not pulling for plants

# Download plant occurrence data from GBIF
```{r}
occ_download(
pred("hasCoordinate", TRUE),
pred("hasGeospatialIssue", FALSE),
pred_in("country",c("EC","CO","VE", "PE", "BO")),
format = "SIMPLE_CSV"
)
```

## Retrive GBIF download, save file, and load into r
```{r}
d1 <- occ_download_get("0097297-230530130749713", path = output_path, overwrite = TRUE) %>%
  occ_download_import()
```

@@

```{r}
print("The number of occurrences is")
nrow(d1)
print("The number of species is" )
length(unique(d1$species))
print("The number of families is" )
length(unique(d1$family))
```

@@

# Write data to csv
```{r}
TropicalAndes_GBIF_path <- file.path(output_path,"TropicalAndes_GBIF_plant_occ.csv") 
write.csv(d2, file = TropicalAndes_GBIF_path)
TropicalAndes_GBIF_species_path <- file.path(output_path,"TropicalAndes_GBIF_plant_species.csv") 
write.csv(GBIF_SpeciesList, file = TropicalAndes_GBIF_species_path)
```

>>>>

# Download plant occurrence data from GBIF
```{r}
occ_download(
pred("taxonKey", 6),
pred("hasCoordinate", TRUE),
pred("hasGeospatialIssue", FALSE),
pred_in("country",c("EC","CO","VE", "PE", "BO")),
format = "SIMPLE_CSV"
)
```

## Retrive GBIF download, save file, and load into r
```{r}
d1 <- occ_download_get("0001452-230918134249559", path = output_path, overwrite = TRUE) %>%
  occ_download_import()
```

@@

```{r}
print("The number of occurrences is")
nrow(d1)
print("The number of species is" )
length(unique(d1$species))
print("The number of genera is" )
length(unique(d1$genus))
print("The number of families is" )
length(unique(d1$family))
```

@@

# Write data to csv
```{r}
TropicalAndes_GBIF_path <- file.path(output_path,"TropicalAndes_GBIF_plant_occ.csv") 
write.csv(d1, file = TropicalAndes_GBIF_path)
TropicalAndes_GBIF_species_path <- file.path(output_path,"TropicalAndes_GBIF_plant_species.csv") 
write.csv(GBIF_SpeciesList, file = TropicalAndes_GBIF_species_path)
```
